Environmental Data Analysis

### 2023-07-10 analysis/env_analysis.Rmd
add study comparison

# create estimation results table
effects_tbl <- draws_filt %>%
  mutate(outcome = recode(as.character(outcome), !!! vars_labels_no_units),
         outcome = factor(outcome, levels = rev(vars_labels_no_units))) %>%
  group_by(outcome) %>%
  mean_qi() %>%
  ungroup() %>%
  filter(.width == .95) %>%
  select(outcome, aircleaner, `.lower`, `.upper`) %>%
  mutate_if(is.numeric, round_k) %>%
  mutate(across(-outcome, tex_sign)) %>%
  arrange(-row_number()) %>%
  mutate(outcome = c("CN", "PM$_{1}$", "PM$_{2.5}$", "PM$_{4}$", "PM$_{10}$")) %>%
  as.matrix() %>%
  xtable() %>%
  print.xtable(
    file = "../results/env-data/estimation-results-table.tex",
    type = "latex",
    sanitize.text.function = identity,
    include.colnames = F,
    include.rownames = F,
    only.contents = T,
    hline.after = NULL)

>>>>

# create estimation results table
effects_tbl <- draws_filt %>%
  mutate(outcome = recode(as.character(outcome), !!! vars_labels_no_units),
         outcome = factor(outcome, levels = rev(vars_labels_no_units))) %>%
  group_by(outcome) %>%
  mean_qi() %>%
  ungroup() %>%
  filter(.width == .95) %>%
  select(outcome, aircleaner, `.lower`, `.upper`) %>%
  mutate_if(is.numeric, round_k) %>%
  arrange(-row_number()) %>%
  mutate(outcome = c("CN", "PM$_{1}$", "PM$_{2.5}$", "PM$_{4}$", "PM$_{10}$")) %>%
  as.matrix() %>%
  xtable() %>%
  print.xtable(
    file = "../results/env-data/estimation-results-table.tex",
    type = "latex",
    sanitize.text.function = identity,
    include.colnames = F,
    include.rownames = F,
    only.contents = T,
    hline.after = NULL)
